Factoring with $n+1$ clean qubits and $n$ dirty qubits

### 2017-04-05 paper.tex
Half-rewritten into high-to-low order

\documentclass[twocolumn]{article}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}
\title{Reversible Modular Addition using a Dirty Bit}
\author{Craig Gidney}

@@

\begin{abstract}
\em
We present size-efficient reversible classical circuits for performing addition, incrementation, comparisons, modular addition, and modular offset on registers of differing sizes using either no ancilla or 1 ancilla in an unknown state.
We improve the number of qubits needed to factor an $n$-bit number from $2n+2$ \cite{takahashi2006, haner2016} to $2n+1$, without increasing the asymptotic cost of the circuit.
\end{abstract}

@@

When constructing quantum circuits, or classical reversible circuits, the number of available ancilla is an important resource.
An ancilla is an extra bit or qubit available for use by a circuit as temporary workspace.
Ancilla may be initialized to a known state (``clean bit"), or be given to the circuit in an unknown state (``dirty bit") that must be restored before the circuit finishes.
Clean bits are more valuable, allowing for simpler and more compact circuit constructions, but dirty bits are more plentiful, because any temporarily unused qubit is a borrowable dirty bit.

Because one part of a circuit can borrow dirty bits from another part of the same circuit, circuit constructions that require only dirty bits are easier to apply under tight space constraints, or on circuit topologies where other ancilla are too far away to be acquired quickly.
For example, H\"{a}ner et al. used dirty bits to improve the cost of performing Shor's algorithm, when limited to using only $2n+2$ qubits and Toffoli based circuits, to $O(n^3)$ depth and $O(n^3 \lg n)$ size \cite{haner2016}.
The modular addition construction in this paper improves on \cite{haner2016} by cutting the number of required qubits to factor an $n$-bit number from $2n+2$ to $2n+1$.

Our paper is structured as follows.
The introduction describes the various sections and also itself for no discernible reason.
Section \ref{sec:review} discusses existing circuit constructions.
In sections \ref{sec:first-circuit} through \ref{sec:last-circuit} we describe various arithmetic circuit constructions that use 0 or 1 dirty bit, building up to modular addition.
We then describe how to use our single-dirty-bit modular addition to factor an $n$ bit number using $2n+1$ qubits in section \ref{sec:applications}.

All constructions assume a 2s-complement representation of integers.
All circuit diagrams have the least significant bit towards the top.
For clarity, circuit diagrams will divide compound operations into separate input and output parts, with inputs shaded gray.

@@

\section{$O(N)$ inline adders} \label{sec:first-circuit}

@@

\begin{figure}
  \centering
  \includegraphics[totalheight=3cm]{inline-adder.png}
  \caption{\em Adder for input and target registers of the same size.
  Requires no ancilla, and uses $O(N)$ gates and depth.
  Based on \cite{van2004, takahashi2005}.}
  \label{fig:inlineadder}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[totalheight=3cm]{inline-adder-into-large.png}
  \caption{\em
      Adder with target larger than source, using no ancilla.
      Uses $O(N)$ gates and depth.
      The increment and decrement gates all have at least one free wire to borrow as a dirty ancilla.}
  \label{fig:inline-adder-into-large}
\end{figure}

@@

A register can be incremented by subtracting both $x$ and $\neg x = -x-1$ from it, for any $x$.
When $N$ dirty bits are available, $x$ can come from a register defined by those $N$ arbitrary bits, as shown in figure \ref{fig:double-sub-increment}.

\begin{figure}
  \centering
  \includegraphics[totalheight=2cm]{double-sub-increment.png}
  \caption{\em Subtracting $x$ and $-x-1$ from a register increments it. Requires $O(N)$ depth, size, and $N$ dirty ancilla.}
  \label{fig:double-sub-increment}
\end{figure}

@@

To work around not being able to operate on the borrowed bits while using them as a control, start with the double-subtraction trick but change the second subtraction to an addition and conditionally toggle the target bits instead of the input bits.
When the condition isn't satisfied, the addition and subtraction will cancel each other.
When the condition is satisfied, the addition will be inverted into a subtraction, and both the subtraction and addition-turned-subtraction will fire, subtracting the input register from the target register twice.
However, because we are conditioning on the input bits all being on, we know the input must be -1.
Therefore the target was incremented by 2.
To halve the +2 into a +1, prepend a dirty least-significant-bit onto the target register as shown in \ref{fig:compact-increment}.

\begin{figure}
  \centering
  \includegraphics[totalheight=1.5cm]{compact-increment.png}
  \caption{\em Odd-sized $O(N)$ increment with 1 dirty ancilla.}
  \label{fig:compact-increment}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[totalheight=2cm]{compact-increment-even.png}
  \caption{\em Even-sized $O(N)$ increment with 1 dirty ancilla.}
  \label{fig:compact-increment-even}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[totalheight=2cm]{controlled-increment-odd.png}
  \caption{\em Odd-sized $O(N)$ controlled increment with 1 dirty ancilla.}
  \label{fig:controlled-increment-odd}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[totalheight=2.5cm]{controlled-increment-even.png}
  \caption{\em Even-sized $O(N)$ controlled increment with 1 dirty ancilla.}
  \label{fig:controlled-increment-even}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[totalheight=1.4cm]{ancilla-bootstrap.png}
  \caption{\em Bootstrapping a dirty ancilla out of an increment gate using quantum operations.
  The $i^{\text{frac}}$ gate is a ``phase gradient" operation that phases each computational basis state $|v\rangle$ by an amount proportional to $v/2^d$, where $d$ is the size of the register.
  In this case each state is phased by $e^{i \frac{\pi}{2} v/2^d}$.
  The phase gradient is implemented by a column of $Z^{2^{-k}}$ gates, .}
  \label{fig:bootstrap-ancilla}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[totalheight=3cm]{comparison-less.png}
  \caption{\em Toggling a target bit if one register is less than another, without using ancilla.}
  \label{fig:comparison-less}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[totalheight=3cm]{comparison-leq.png}
  \caption{\em Toggling a target bit if one register is less than or equal to another, without using ancilla.}
  \label{fig:comparison-leq}
\end{figure}

@@

A pivot-flip operation reverses the order of states less than or equal to a given pivot value.
For example, a pivot-flip with the pivot equal to 3 would swap $|0\rangle$ and $|3\rangle$, swap $|1\rangle$ and $|2\rangle$, and leave all other states untouched.
Pivot-flips are useful for implementing cyclic operations, such as modular addition.

$$\text{PivotFlip}_k = \sum_{i=0}^k |k-i\rangle \langle i| + \sum_{i=k+1}^{N-1} |i\rangle \langle i|$$

And the overall permutation, including the pivot input, is:

$$\text{PivotFlip} = \sum_{k=0}^{N-1} |k\rangle \langle k| \otimes \text{PivotFlip}_{k}$$

To perform a pivot-flip efficiently, we use the fact that $x \rightarrow \lnot(x - a - 1)$ nearly does what is required.
As shown in figure \ref{fig:double-flip}, the permutation $x \rightarrow \lnot(x - a - 1)$ flips the range below-and-including the pivot but also flips the range above the pivot.
However, because $x \rightarrow \lnot(x - a - 1)$ is its own inverse and doesn't change whether any value is less than or equal to the pivot, the operation can be controlled by dirty comparisons against the pivot.

By applying $x \rightarrow \lnot(x - a - 1)$ twice, controlled by a dirty bit that is toggled by the comparison, the desired effect is achieved.
For states that are less than or equal to the pivot $a$, the dirty ancilla is being toggled and exactly one of the controlled flips will happen.
For other states, the ancilla does not change and so the controlled flip happens no times or two times, undoing itself.
See figure \ref{fig:const-pivot-flip} fot the construction, as well as a variant that only flips values strictly less than the pivot instead of including the pivot.

\begin{figure}
  \centering
  \includegraphics[totalheight=4cm]{double-flip.png}
  \caption{\em Subtraction followed by logical negation performs flips both above and below $k$.}
  \label{fig:double-flip}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[totalheight=4.5cm]{pivot-flip.png}
  \caption{\em Pivot flip circuits.
  When the top wire bundle is a register, the subtractions are controlled by adding a control to any CNOTs, increments, and decrements in figures \ref{fig:inlineadder} or \ref{fig:inline-adder-into-large}.
  When the top wire bundle is a compile-time constant, the subtractions use the construction from \cite{haner2016} and are controlled as shown in figure \ref{fig:controlled-offset}.}
  \label{fig:const-pivot-flip}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[totalheight=3.1cm]{controlled-offset.png}
  \caption{\em Offset circuit from \cite{haner2016}, modified to include a control.}
  \label{fig:controlled-offset}
\end{figure}

@@

A modular addition is three pivot flips.
To add $a$ into a register modulo $r$, perform pivot-flips with the pivot at $r-1-a$, then $r-1$, then $a-1$.
See figure \ref{fig:modular-add}.

\begin{figure}
  \centering
  \includegraphics[totalheight=1.4cm]{modular-addition.png}
  \caption{\em Modular addition circuit.
  The $+r$ operations are offset gates requiring $O(N \lg N)$ size when the modulus is a constant.
  The pivot-flips require a dirty bit.}
  \label{fig:modular-add}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[totalheight=16cm]{modular-add-graph.png}
  \caption{\em
      Dependency graph of constructions used to create a classical reversible modular adder / modular offset gates using only 1 dirty bit.}
  \label{fig:modular-dependencies}
\end{figure}

@@

>>>>

\documentclass[twocolumn]{article}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}
\title{Factoring with $n+1$ clean qubits and $n$ dirty qubits}
\author{Craig Gidney}

@@

\begin{abstract}
\em
We present size-efficient reversible classical circuits for performing various arithmetic operations aided by ancilla in an unknown state.
We improve the number of qubits needed to factor an $n$-bit number from $2n+2$ clean qubits \cite{takahashi2006, haner2016} to $n+1$ clean qubits and $n$ dirty qubits, without increasing the asymptotic size or depth of the circuit.
\end{abstract}

@@

When constructing quantum circuits, or classical reversible circuits, the number of available ancilla is an important resource.
An ancilla is an extra bit or qubit available for use by a circuit as temporary workspace.
Ancilla may be initialized to a known state (``clean bit"), or be given to the circuit in an unknown state (``dirty bit") that must be restored before the circuit finishes.
Clean bits are more valuable, allowing for simpler and more compact circuit constructions, but dirty bits are more plentiful, since any temporarily unused bit is a borrowable dirty bit.

Because one part of a circuit can borrow dirty bits from another part of the same circuit, circuit constructions that require only dirty bits are easier to apply under tight space constraints, or on circuit topologies where other ancilla are too far away to be acquired quickly.
For example, in \cite{haner2016} H\"{a}ner et al. used dirty bits to improve the cost of performing Shor's algorithm, when limited to using only $2n+2$ qubits and Toffoli based circuits, from ??????? to $O(n^3)$ depth and $O(n^3 \lg n)$ size.
The construction in this paper improve on \cite{haner2016} by cutting the number of required qubits to factor an $n$-bit number from $2n+2$ to $2n+1$.

Our paper is structured as follows.
The introduction describes the various sections and also itself for no discernible reason.
Section \ref{sec:review} discusses existing circuit constructions for various arithmetic tasks.
In section \ref{sec:construct} we iteratively reduce period finding into simpler and simpler arithmetic operations, until we reach constant-sized gates, while tracking the number of required dirty ancilla.
Then, in section \ref{sec:costs}, we discuss the novelty and comparative costs of the presented arithmetic circuit constructions.
Finally, \ref{sec:conclusions} concludes and summarizes.

All circuit daigrams assume a 2s-complement representation of integers, and have the least significant bit towards the top.
For clarity, circuit diagrams will divide compound operations into separate input and output parts, with inputs shaded gray.

@@

\subsection{Period Finding}

...

\section{From Period Finding to Toffolis, using $2n+1$ qubits} \label{sec:first-circuit} \label{sec:construct}

\subsection{Period Finding}

We begin with the abstract period finding circuit from ???, shown in figure \ref{fig:period-finding-solo-phase-qubit}.
This circuit uses (a) controlled modular multiplication, (b) measurement, (c) X-axis rotations parametrized by previous measurements, and (d) qubit resets.
The only non-trivial operation is (a), controlled modular multiplication an $m$ qubit register, for which we will need $m$ clean ancilla.

\begin{figure}
  \centering
  \makebox[\linewidth]{
    \includegraphics[width=\linewidth]{assets/shor-period-finding.png}
  }
  \caption{\em
	High-level period finding circuit [[[ cite ]]].
    The triangle indicates how many ancilla are needed, by our constructions, to perform the linked operation.
  }
  \label{fig:period-finding}
\end{figure}

\begin{figure*}
  \centering
  \makebox[\linewidth]{
    \includegraphics[width=\linewidth]{assets/shor-period-finding-solo-phase-qubit.png}
  }
  \caption{\em
	Period finding with a single phase-estimation qubit [[[ cite ]]].
	The small $\tiny \oplus$ are ``X-axis controls".
	An X-axis control is equivalent to a normal control, but with a Hadamard gate applied before and after.
	It conditions on the state $\frac{1}{\sqrt 2}|0\rangle - \frac{1}{\sqrt 2}|1\rangle$ instead of on the state $|1\rangle$.
  }
  \label{fig:period-finding-solo-phase-qubit}
\end{figure*}

\subsection{Controlled Modular Multiply}

We do controlled modular multiplication with the same technique used in ???: multiply-accumulate into an extra register, then erase the input with an inverse multiply-accumulate.
See figure \ref{fig:controlled-modular-multiply}.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/controlled-modular-multiply.png}
  \caption{\em
    Reducing a controlled modular multiplication into two controlled modular multiply-accumulates.
    Based on ???.
  }
  \label{fig:controlled-modular-multiply}
\end{figure}

The controlled modular multiply-accumulates require no ancilla.

\subsection{Controlled Modular Multiply-Accumulate}

To perform multiply-accumulation, we use a shift-and-add algorithm.
We right-shift (i.e. divide by 2) the target register $m-1 {\pmod R}$ times, then begin iteratively left-shifting (i.e. multiplying by 2) and conditionally adding $K$ into the target based on the appropriate input bit.
See figure \ref{fig:controlled-modular-multiply-accumulate}.

Both the modular bit-shift and conditional offset operations require a single dirty bit, but have more than enough available to borrow.
Also, both operations will be implemented in terms of what we call a pivot flip operation.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/controlled-modular-multiply-accumulate.png}
  \caption{\em
    Reducing a controlled modular multiply-accumulate into multiplications by 2 and controlled modular additions.
    Note that, although the controlled modular offset operations require a dirty ancilla, they can borrow it from one of the wires they don't affect.
    Based on ???.
  }
  \label{fig:controlled-modular-multiply-accumulate}
\end{figure}

\subsection{Pivot-Flip}

A "pivot-flip" is an operation that reverses the order of states less than a given pivot value, without affecting other states.
For example, a pivot-flip with the pivot equal to 4 would swap $|0\rangle$ and $|3\rangle$, swap $|1\rangle$ and $|2\rangle$, and leave all other states untouched.
Pivot-flips are useful for implementing cyclic operations, such as modular addition.

$$\text{PivotFlip}_k = \sum_{i=0}^{k-1} |k-i-1\rangle \langle i| + \sum_{i=k}^{N-1} |i\rangle \langle i|$$

To perform a pivot-flip efficiently, we use the fact that $x \rightarrow \lnot(x - a)$ nearly does what is required.
As shown in figure \ref{fig:double-flip}, the permutation $x \rightarrow \lnot(x - a)$ flips the range below $a$ but also flips the range above-and-including $a$.
However, because $x \rightarrow \lnot(x - a)$ is its own inverse and doesn't change whether any value is less than the pivot, the operation can be controlled by a dirty ancilla being toggled by a comparison against $a$.

See figure \ref{fig:const-pivot-flip} for the construction (as well as a less-than-or-equal-to-pivot variant).
For states that are less than the pivot $a$, the dirty ancilla is being toggled so exactly one of the controlled flips will happen.
For other states, the ancilla does not change and so the controlled flip happens either no times or two times (undoing itself) for a net effect of no effect.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/double-flip.png}
  \caption{\em Subtraction followed by logical negation performs flips both above and below $k$.}
  \label{fig:double-flip}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/pivot-flip.png}
  \caption{\em Pivot flip circuits.
  When the top wire bundle is a register, the subtractions are controlled by adding a control to any CNOTs, increments, and decrements in figures \ref{fig:inlineadder} or \ref{fig:inline-adder-into-large}.
  When the top wire bundle is a compile-time constant, the subtractions use the construction from \cite{haner2016} and are controlled as shown in figure \ref{fig:controlled-offset}.}
  \label{fig:const-pivot-flip}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/controlled-offset.png}
  \caption{\em Offset circuit from \cite{haner2016}, modified to include a control.}
  \label{fig:controlled-offset}
\end{figure}

\subsection{Modular Doubling}

If the modulus $R$ is even, modular doubling is irreversible and therefore not unitary (it can be performed, but it must create garbage bits leading to decoherence).
So we assume that the modulus $R$ is odd.

To multiply a register by 2, we use a pivot-flip operation, a subtraction, and CNOTs.
See \ref{fig:modular-double}.
This construction requires a dirty ancilla because the pivot-flip operation covers all wires but requires a dirty ancilla.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/modular-double.png}
  \caption{\em
    Modular doubling.
    Assumes $R$ is odd.
    Requires 1 dirty ancilla.
    Trashes out-of-range values (ones greater or equal to $R$).
  }
  \label{fig:modular-double}
\end{figure}

https://arxiv.org/abs/1202.6614

https://arxiv.org/abs/1110.2574

[[[diagram of their construction]]]

[[[diagram of their doubling]]]

The construction requires $n+1$ clean ancilla.
$n$ for the second register, and $1$ for holding a carry bit during the doubling step.
By using the doubling construction in figure [[[whatever]]], the extra ancilla can be dirty instead of clean.

[[[diagram of my doubling]]]

xxx

\subsection{Controlled Modular Addition}

As shown in figure \ref{fig:mod-add-from-pivot-flip-bars}, a modular addition is three pivot flips.
To add $a$ into a register modulo $r$, perform pivot-flips with the pivot at $r-1-a$, then $r-1$, then $a-1$.
See figure \ref{fig:modular-add} for the circuit.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/mod-add-from-pivot-flip-bars.png}
  \caption{\em
     A modular offset is three pivot flips.
     One at $r-a$, then one at $r$, then one at $a$.
   }
  \label{fig:modular-add}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/modular-addition.png}
  \caption{\em Reducing modular addition to non-modular offset, pivot-flips, and NOTs.}
  \label{fig:modular-add}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/controlled-modular-addition.png}
  \caption{\em Reducing controlled modular addition to non-modular offset, controlled pivot-flips, and NOTs.}
  \label{fig:modular-add}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/modular-offset.png}
  \caption{\em Reducing modular offset to non-modular offset, controlled pivot-flips, and NOTs.}
  \label{fig:modular-add}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/controlled-modular-offset.png}
  \caption{\em Reducing controlled modular offset to non-modular offset, controlled pivot-flips, and NOTs.}
  \label{fig:modular-add}
\end{figure}

\section{$O(N)$ inline adders}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/inline-adder.png}
  \caption{\em Adder for input and target registers of the same size.
  Requires no ancilla, and uses $O(N)$ gates and depth.
  Based on \cite{van2004, takahashi2005}.}
  \label{fig:inlineadder}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/inline-adder-into-large.png}
  \caption{\em
      Adder with target larger than source, using no ancilla.
      Uses $O(N)$ gates and depth.
      The increment and decrement gates all have at least one free wire to borrow as a dirty ancilla.}
  \label{fig:inline-adder-into-large}
\end{figure}

@@

A register can be incremented by subtracting both $x$ and $\neg x = -x-1$ from it, for any $x$.
When $N$ dirty bits are available, $x$ can come from a register defined by those $N$ arbitrary bits, as shown in figure \ref{fig:increment-many-dirty}.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/increment-many-dirty.png}
  \caption{\em Subtracting $x$ and $-x-1$ from a register increments it. Requires $O(N)$ depth, size, and $N$ dirty ancilla.}
  \label{fig:increment-many-dirty}
\end{figure}

@@

To work around not being able to operate on the borrowed bits while using them as a control, start with the double-subtraction trick but change the second subtraction to an addition and conditionally toggle the target bits instead of the input bits.
When the condition isn't satisfied, the addition and subtraction will cancel each other.
When the condition is satisfied, the addition will be inverted into a subtraction, and both the subtraction and addition-turned-subtraction will fire, subtracting the input register from the target register twice.
However, because we are conditioning on the input bits all being on, we know the input must be -1.
Therefore the target was incremented by 2.
To halve the +2 into a +1, prepend a dirty least-significant-bit onto the target register as shown in \ref{fig:increment-odd}.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/increment-odd.png}
  \caption{\em Odd-sized $O(N)$ increment with 1 dirty ancilla.}
  \label{fig:increment-odd}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/increment-even.png}
  \caption{\em Even-sized $O(N)$ increment with 1 dirty ancilla.}
  \label{fig:increment-even}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/controlled-increment-odd.png}
  \caption{\em Odd-sized $O(N)$ controlled increment with 1 dirty ancilla.}
  \label{fig:controlled-increment-odd}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/controlled-increment-even.png}
  \caption{\em Even-sized $O(N)$ controlled increment with 1 dirty ancilla.}
  \label{fig:controlled-increment-even}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/ancilla-bootstrap.png}
  \caption{\em Bootstrapping a dirty ancilla out of an increment gate using quantum operations.
  The $i^{\text{frac}}$ gate is a ``phase gradient" operation that phases each computational basis state $|v\rangle$ by an amount proportional to $v/2^d$, where $d$ is the size of the register.
  In this case each state is phased by $e^{i \frac{\pi}{2} v/2^d}$.
  The phase gradient is implemented by a column of $Z^{2^{-k}}$ gates, .}
  \label{fig:bootstrap-ancilla}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/comparison-less.png}
  \caption{\em Toggling a target bit if one register is less than another, without using ancilla.}
  \label{fig:comparison-less}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/comparison-leq.png}
  \caption{\em Toggling a target bit if one register is less than or equal to another, without using ancilla.}
  \label{fig:comparison-leq}
\end{figure}

@@

@@

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/modular-add-graph.png}
  \caption{\em
      Dependency graph of constructions used to create a classical reversible modular adder / modular offset gates using only 1 dirty bit.}
  \label{fig:modular-dependencies}
\end{figure}

To perform modular multiplication, we use the construction from [[[[ reference ]]], which works by iteratively scaling and adding the target register into an ancilla register.
The ancilla and target register then switch roles, and the old target register is erased by adding in the new target times a  multiplicative inverse.

@@

[[[ diagram of Shor's algorithm ]]]
